Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
improved use case table caption

Solid circles (\textbullet) indicate required metadata, while open circles (\textopenbullet) indicate recommended metadata.

>>>>

Solid circles (\textbullet) indicate that the use case depends on that metadata, while open circles (\textopenbullet) indicate that the use case would benefit from that metadata if available.
